Developing a Bubble Chamber Particle Discriminator Using Semi-Supervised Learning

### 2019-03-02 documentation/report.tex
Grammar edits

    \item Gravitational Differentiation is an analog alternative to Iterative Clustering. Using a novel piecewise exponential function for calculating final-layer derivatives, called $\mathrm{GravDiff}(p, \psi, g)$, unlabeled examples are caused to "gravitate" toward more accurate predictions based on the confidence of the neural network's predictions.

@@

Semi-supervised learning produced better accuracy than supervised learning. Gravitational differentiation was the best overall model, achieving 99.7\% accuracy on validation data and 98.3\% on test data. This confirms my hypothesis; it is indeed beneficial to train on the neural network's most confident predictions.

@@

These results confirm that I met my objective: my new techniques successfully addressed the two fundamental challenges I identified, permitting significantly improved performance, requiring little manual analysis or optimization.

@@

On DEAP-3600, my cylindrical projection, combined with a 2D CNN, performed better than the conventional classifier on simulated data, reducing the WIMP misclassification rate from 91.0\% to 75.7\% while matching the conventional classifier's 99.6\% background removal rate. Additionally, the predictions made on real-world data demonstrate clear potential. Differences between the simulated and real-world data provide potentially useful diagnostic information on the DEAP-3600 simulation (assuming that WIMPs are not present).

>>>>

    \item Gravitational Differentiation is an analog alternative to Iterative Clustering. Using a novel piecewise exponential function for calculating final-layer derivatives, called $\mathrm{GravDiff}(p, \psi, g)$, unlabeled examples are caused to ``gravitate'' toward more accurate predictions based on the confidence of the neural network's predictions.

@@

Semi-supervised learning produced better accuracy than supervised learning. Gravitational Differentiation was the best overall technique, achieving 99.7\% accuracy on validation data and 98.3\% on test data. This confirms my hypothesis; it is indeed beneficial to incorporate the neural network's most confident predictions into its training data.

@@

These results confirm that I met my objective: my new techniques successfully addressed the two fundamental challenges I identified, permitting significantly improved performance while requiring little manual analysis or optimization.

@@

On DEAP-3600, my cylindrical projection, combined with a 2D CNN, performed better than the conventional classifier on simulated data, reducing the WIMP misclassification rate from 91.0\% to 75.7\% while matching the conventional classifier's 99.6\% background removal rate. Additionally, the predictions made on real-world data demonstrate clear potential. Differences between the simulated and real-world data provide potentially important diagnostic information on the DEAP-3600 simulation (assuming that WIMPs are not present).
